---
title: "Assignment1"
author: "Kirram"
date: "October 17, 2015"
output: html_document
---

This report was produced to represent answers to the questions in the Peer Assessment 1 of Reproducible Research Class.

Libraries required:

```{r, echo=TRUE}
  library(ggplot2)
  library(plyr)
```

1.  Loading and preprocessing the data

    Show any code that is needed to

    Load the data (i.e. read.csv())

```{r, echo=TRUE}
  data1<-read.csv("activity.csv")
```


    Process/transform the data (if necessary) into a format suitable for your analysis
    
    For question 1, we need to sum up numbers of steps for each day:
    
```{r, echo=TRUE}
  data_q1<-ddply(data1, .(date),summarise, SumSteps=sum(steps))

```
    
    For question 2, we need to average numbers of steps for each interval:

```{r, echo=TRUE}
  data_q2<-ddply(data1, .(interval), summarise, Mean=mean(steps, na.rm = TRUE)) 

```

Q1. What is mean total number of steps taken per day?

    For this part of the assignment, you can ignore the missing values in the dataset.
    
    Make a histogram of the total number of steps taken each day
    
    
```{r, echo=TRUE}
  q1<-ggplot(data_q1, aes(x=date, y=SumSteps))+geom_histogram(stat = "identity")
  q1
```

    Calculate and report the mean and median total number of steps taken per day
Mean: 

```{r, echo=TRUE}
mean_q1<-mean(data_q1$SumSteps, na.rm = TRUE)
mean_q1
```

Median:
```{r,echo=TRUE}
median_q1<-median(data_q1$SumSteps, na.rm=TRUE)
median_q1
```



Q2. What is the average daily activity pattern?

  Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average      number of steps taken, averaged across all days (y-axis)
```{r, echo=TRUE}
  q2<-ggplot(data_q2)+geom_freqpoly(aes(x=interval,y=Mean), stat="identity")  
  q2
```
  
  Which 5-minute interval, on average across all the days in the dataset, contains the maximum     number of steps?

```{r, echo=TRUE}

  data_q2_sorted<-arrange(data_q2, by=Mean, decreasing=TRUE)
  data_q2_max<-data_q2_sorted[1:1,]
  data_q2_max
```




